Introducing statistics with `intRo`

### 2016-01-24 jcgs-paper-2016/paper.Rmd
Fix some typos

Upon the release of \texttt{RStudio}'s \texttt{Shiny} [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call \texttt{intRo}, available at http://www.intro-stats.com. \texttt{intRo} offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest. Additionally, \texttt{intRo} stands apart from new tols in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text.

@@

\texttt{intRo} is a web-based tool to accompany an introductory statistics class. It is meant to assist in the learning of statistics rather than a stand-alone deliverer of statistics education, with the intention of being used in conjunction with a guided class. An accompanying R package, titled \texttt{intRo} and available on GitHub, assists in the downloading, running, and deploying of \texttt{intRo} instances.

We have three fundamental philosophies that guided the creation of \texttt{intRo}, and this comes out in the design. Primarily, \texttt{intRo} is \emph{easy} to use and can be an \emph{exciting} part of learning statistics. Additionally, \texttt{intRo} is an \emph{extensible} tool, allowing for a user of \texttt{intRo} to tailor the tool for her own classroom needs.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{images/user_experience.pdf}
\caption{Typical user experience of generating a result in \texttt{intRo}. In this instance, a mosaic plot (and its corresponding code) was created and saved to the final compendium.}
\label{fig:user_experience}
\end{figure}

@@

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{sec:extensible}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.

>>>>

Upon the release of \texttt{RStudio}'s \texttt{Shiny} [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call \texttt{intRo}, available at http://www.intro-stats.com. \texttt{intRo} offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest. Additionally, \texttt{intRo} stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text.

@@

\texttt{intRo} is a web-based tool to accompany an introductory statistics class. It is meant to assist in the learning of statistics rather than act as a stand-alone deliverer of statistics education, with the intention of being used in conjunction with a guided class. An accompanying R package, titled \texttt{intRo} and available on GitHub, assists in the downloading, running, and deploying of \texttt{intRo} instances.

We have three fundamental philosophies that guided the creation of \texttt{intRo}. In particular, \texttt{intRo} is \emph{easy} to use and can be an \emph{exciting} part of learning statistics. Additionally, \texttt{intRo} is an \emph{extensible} tool, allowing for a user of \texttt{intRo} to tailor the tool for his or her own classroom needs.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{images/user_experience.pdf}
\caption{A typical user experience of generating a result in \texttt{intRo}. In this instance, a mosaic plot (and its corresponding code) was created and saved to the final compendium.}
\label{fig:user_experience}
\end{figure}

@@

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{sec:extensible} and section \ref{sec:modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.
